Social Visual Analytics: DevOps for Data Scientists

### 2015-01-28 conclusion.tex
yes

We described the motivation introducing web technologies
for searching, collaborating, recommending, publishing
reusable notebooks as part of the visual analytics process.
We implemented these ideas in the RCloud prototype.
Rcloud assists software development and release using
an approach similar to DevOps in web services.
Experience with the prototype provided evidence that
data science teams, and the organizations in which they work,
benefit from having such capabilities.

Future work will address cross-language development,
source code analysis, richer recommendation techniques,
and improvements to the HTML5 front end.

>>>>

We presented a case for a visual analytics environment that supports
the entire work process, from exploratory data analysis
through development and production deployment. One might think of
this as ``DevOps for data science.'' The environment supports
collaboration and communication, with capabilities for
creating and sharing experimental workbooks, version control,
searching, recommending, annotating, and deploying experiments
as web sites and reusable services.

We implemented these ideas in the RCloud prototype.
Experience with the prototype provided evidence that data
science teams, and the organizations in which they work,
benefit from having such capabilities.

Reasonable next steps are to support cross-language development,
richer source code analysis and recommendation techniques, and
improvements to the HTML5 human interface.
